\textbf{AI Engineer – Akunah} \hfill \textit{2026 – present} \\
\textit{Healthcare Technology / Orthopaedic Surgery Research (Full-time, Brisbane QLD)} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Developing and deploying ML models for orthopaedic surgery outcome prediction, integrating structured and unstructured clinical data.
    \item Implementing AI algorithms across NLP and computer vision domains to support surgical research and clinical decision-making.
    \item Collaborating with surgeons, data scientists, and engineers to deliver production-grade AI solutions aligned with medical compliance requirements.
    \item Contributing to model monitoring, hyperparameter tuning, and optimization to ensure reliability and performance in clinical environments.
\end{itemize}

\vspace{0.1em}

\textbf{AI \& Data Engineer – Assembly} \hfill \textit{2026 – present} \\
\textit{Technology (Remote, Contractor)} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Architected cloud infrastructure using AWS CDK, building modular and reusable constructs to support scalable event-driven data solutions.
    \item Designed and implemented the sensor-events pipeline for ingesting, transforming, and serving high-volume sensor data across platforms and data stores.
    \item Leading real-time streaming architecture development for low-latency data processing, enabling live data consumption and downstream analytics.
    \item Owned end-to-end AI/data solution lifecycle — from requirements and architecture design through implementation, testing, and production deployment.
\end{itemize}

\vspace{0.1em}

\textbf{Tech Lead / Data Engineering – BPT} \hfill \textit{2024 – 2026} \\
\textit{Government Tax Authority (SUNAT Peru), Pension Funds, Healthcare \& Social Services, Oil \& Gas, Logistics, Government Tax Authority, Banking} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Leading real-time data pipeline implementation for SUNAT (Peru's National Tax Administration), processing large-scale financial transaction data with strict government compliance requirements including CDC and streaming architectures.
    \item Designed scalable data architectures improving performance by 10\%; automated ETL processes reducing processing time by 40\%.
    \item Integrated structured/unstructured data sources; deployed ML models using MLflow improving accuracy by 5\%.
    \item Managed client relationships (95\% satisfaction); developed Azure Data Factory pipelines.
    \item Built interactive conversational interface allowing teams to query data using natural language, leveraging LLMs and Databricks Genie to democratize data access.
\end{itemize}

\vspace{0.1em}

\textbf{AI Engineer \& Data Consultant – DeltaWits} \hfill \textit{2023 – 2026} \\
\textit{Healthcare Technology (Remote)} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Architected AI-powered healthcare solutions using AWS Bedrock and LLMs, reducing physician prep time by 40\% through automated medical data processing.
    \item Developed intelligent medical profile generators integrating structured/unstructured health data, saving clinicians 10 minutes per consultation.
    \item Built scalable, compliant cloud infrastructure on AWS for high-volume medical data processing.
\end{itemize}

\vspace{0.1em}

\textbf{Data Scientist – Botero Soto} \hfill \textit{2023 – 2024} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Led predictive modeling across cloud/on-premise environments using Azure and Databricks, achieving 30\% response time improvement.
    \item Designed scalable analytics solutions and Power BI dashboards; automated processes with code and Power Automate.
    \item Led cross-functional teams delivering data-driven insights and KPI implementations.
\end{itemize}

\vspace{0.1em}

\textbf{Project Leader – Botero Soto} \hfill \textit{2018 – 2023} \\[-0.6em]
\begin{itemize}[leftmargin=*]
    \item Managed optimization projects using agile methodologies; recognized for best operations performance (2020).
    \item Built Power BI dashboards and implemented traceability systems for enhanced data analysis.
    \item Supervised teams of up to 45 people; implemented high-efficiency logistics programs.
\end{itemize}